---
title: "Supplemental. Traut et al., in sub."
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    source_code: embed
    theme: flatly
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard) #general pckgs
library(tidyr)
library(dplyr)
library(shiny)
library(meta)          #meta specific
library(metafor)
library(DT)            #visualization
library(ggplot2)
library(plotly)
library(metaviz) 
library(MASS)
library(gridExtra)
```

```{r functions}
## Function 1: Multilevel Model Variance Breakdown
variance.distribution.3lm <- function(data, m){
  
  # Calculate estimated sampling variance and proportions across levels  
  data <- data
    m <- m
    n <- length(data$v)
    vector.inv.var <- 1/(data$v)
    sum.inv.var <- sum(vector.inv.var)
    sum.sq.inv.var <- (sum.inv.var)^2
    vector.inv.var.sq <- 1/(data$v^2)
    sum.inv.var.sq <- sum(vector.inv.var.sq)
    num <- (n-1)*sum.inv.var
    den <- sum.sq.inv.var - sum.inv.var.sq
    est.samp.var <- num/den
    level1<-((est.samp.var)/(m$sigma2[1]+m$sigma2[2]+est.samp.var)*100)
    level2<-((m$sigma2[1])/(m$sigma2[1]+m$sigma2[2]+est.samp.var)*100)
    level3<-((m$sigma2[2])/(m$sigma2[1]+m$sigma2[2]+est.samp.var)*100)
    Level<-c("level 1", "level 2", "level 3")
    Variance<-c(level1, level2, level3)
    df<-data.frame(Level, Variance)
    df1<-df
    colnames(df1) <- c("Level", "% of total variance")
    
  #Generate plot
  df$distribution<-"Distribution"
  df$Level<-factor(df$Level, levels(df$Level)[c(3,2,1)])
  g <- ggplot(df, aes(fill=Level, y=Variance, x=distribution)) + 
    geom_bar(stat="identity", position="fill", width = 0.3) + coord_flip(ylim = c(1,0)) + scale_y_continuous(labels = scales::percent)+
      theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.ticks.y=element_blank(),
        axis.text.y = element_blank(),
        axis.line.x = element_line(colour = "black",
                                   size = 0.5, linetype = "solid"),
        legend.position = "bottom",
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        legend.background = element_rect(linetype="solid",
                                         colour ="black"),
        legend.title = element_blank(),
        legend.key.size = unit(0.75,"cm")) + guides(fill = guide_legend(reverse = TRUE))
  return(list(g, df1))
}

  funFunnel <- function(x) {
      alpha <- .05
      CRIT_95 <- 1.96
      CRIT_99 <- 2.58
    
      d <- data.frame(se = sqrt(x$vi), es = x$yi, n = attr(x$yi, 'slab'))
      center <- mean(d$es)
      xlabel <- "\nEffect Size"
      ylabel <- "Standard Error\n"

    lower_lim <- max(d$se) + .05 * max(d$se)
    funnel95 <- data.frame(x = c(center - lower_lim * CRIT_95, center,
                                 center + lower_lim * CRIT_95),
                           y = c(-lower_lim, 0, -lower_lim),
                           stringsAsFactors = FALSE)

    left_lim99 <- ifelse(center - lower_lim * CRIT_99 < min(d$es),
                         center - lower_lim * CRIT_99,
                         min(d$es))
    right_lim99 <- ifelse(center + lower_lim * CRIT_99 > max(d$es),
                          center + lower_lim * CRIT_99,
                          max(d$es))
    funnel99 <- data.frame(x = c(center - lower_lim * CRIT_99, center,
                                 center + lower_lim * CRIT_99),
                           y = c(-lower_lim, 0, -lower_lim),
                           stringsAsFactors = FALSE)

    p <- ggplot(d) +
      geom_polygon(aes(x = x, y = y), data = funnel95, alpha = .5,
                   fill = "white") +
      geom_polygon(aes(x = x, y = y), data = funnel99, alpha = .5,
                   fill = "white") +
      geom_point(aes_string(x = "es", y = "-se", text = "n")) +
      geom_vline(aes(), xintercept = center, linetype = "dotted", color = "black") +
      xlab(xlabel) +
      ylab(ylabel) +
     # scale_colour_solarized(name = "", labels = labels, guide = guide) +
      scale_x_continuous(limits = c(left_lim99, right_lim99)) +
      scale_y_continuous(labels = function(x){abs(x)}) +
      theme(panel.background = element_rect(fill = "grey"),
            panel.grid.major =  element_line(colour = "darkgrey", size = 0.2),
            panel.grid.minor =  element_line(colour = "darkgrey", size = 0.5))

    # ggplotly hack - avoid weird lines by preventing overlapping geom_vlines
    if (center != 0) {
      p <- p + geom_vline(aes(), xintercept = 0, linetype = "dashed", color = "grey")
    }

    ggplotly(p, tooltip = c("n", "es")) %>%
      layout(showlegend = FALSE)
  }
  
#Interactive Forest Plot
  forest <- function(inp, x) {
    alpha <- .05
    CRIT_95 <- 1.96
    CRIT_99 <- 2.58
    
    f <- fitted(x)
    p <- predict(x)
    s <- summary(x)

    forest_data <- data.frame(effects = as.numeric(x$yi.f), variances = x$vi.f, 
                              stringsAsFactors = FALSE) %>%
      
      mutate(effects.cil = effects - qnorm(alpha / 2, lower.tail = FALSE) * sqrt(variances),
             effects.cih = effects + qnorm(alpha / 2, lower.tail = FALSE) * sqrt(variances),
             estimate = as.numeric(f),
             short_cite = names(f),
             estimate.cil = p$ci.lb,
             estimate.cih = p$ci.ub,
             inverse_vars = 1/variances,
             identity = 1) %>%
      mutate(short_cite = factor(short_cite, levels = short_cite))
    
      forest_data$short_cite <- paste0(forest_data$short_cite, 
          "  [", round(forest_data$effects.cil,2), ", ", round(forest_data$effects.cih,2),"]")
    
    labels <- NULL
    guide <- FALSE
  
    srt <- pull(forest_data, inp)
    
    plt <- ggplot(data = forest_data, aes(text = effects)) +
      geom_point(aes(x = reorder(short_cite, srt), y = effects, size = inverse_vars)) +
      geom_linerange(aes(x = reorder(short_cite, srt), y = effects, ymin = effects.cil, ymax = effects.cih)) +
      geom_point(aes_string(x = "short_cite", y = "estimate"),
                 shape = 17, colour = "cornflowerblue") +
      geom_linerange(aes_string(x = "short_cite", y = "estimate", ymin = "estimate.cil",
                                ymax = "estimate.cih"), colour = "cornflowerblue", alpha = 0.70) +
      #geom_hline(yintercept = 0, linetype = "dashed", color = "red", size = 1) +
      coord_flip() +
      scale_size_continuous(range = c(1, 3), guide = FALSE) +
      xlab("") +
      ylab("Fisher's Z Transformed Correlation Coefficient") 

    
    ggplotly(plt, tooltip = c("text")) %>%
                      layout(showlegend = FALSE)
  }

```

```{r data}
df <- read.csv('data/20201102_tpfkam_postcomps.csv', header = TRUE)      #readin data
df <- df[df$approach != "both", ]                                        #exclude studies that did both approaches

dat <- escalc(measure="ZCOR",                                            #Raw Correlations - fisher z-transformed
              ri=df$r, 
              ni=df$n, 
              data=df)
```

```{r}
#Model 1a
res.ml <- rma.mv(yi, vi, 
                 random = list(~1 |id, ~1 | paper), 
                 slab=paste(paper), 
                 data=dat)
```

```{r aggregated_data, warning=FALSE}
foo <- df[match(unique(df$paper), df$paper),]                        #ensure match id for each individual paper
bar <- cbind(foo,aggregate(df, by = list(df$paper), FUN = mean))     #calc mean across r and n for each individual paper
df_ag <- bar[,c(1,2,10,11,5,6)]                                      #select relevant cols only

dat_ag <- escalc(measure="ZCOR", #Aggregated Correlations
              ri=df_ag$r, 
              ni=df_ag$n, 
              data=df_ag)
```

```{r aggmodel}
resAgg <- rma(yi, vi, 
              slab=paste(paper), 
              data=dat_ag)
```

Intro
===
Column 
-----------------------------------------------------------------------
### Description

This document presents interactive supplementary analysis reports for Traut et al., in submission at Frontiers in Psychology. Please contact H.J. Traut with any questions (hilary.traut@colorado.edu).


Column {.tabset}
-----------------------------------------------------------------------
### Sample Effects

```{r}
samp <- MASS::mvrnorm(100, mu = c(0,0), Sigma = matrix(c(1,-0.7,-0.7,1), ncol = 2))
samp <- as.data.frame(samp)

p1 <- ggplot(samp, aes(x = V2, y = V1)) + geom_point() + geom_smooth(method = "lm") + 
  labs(title = "Compensation", x = "Baseline Score", y = "Gains")
```

```{r}
samp <- MASS::mvrnorm(100, mu = c(0,0), Sigma = matrix(c(1,0.7,0.7,1), ncol = 2))
samp <- as.data.frame(samp)

p2<- ggplot(samp, aes(x = V2, y = V1)) + geom_point() + geom_smooth(method = "lm") +
  labs(title = "Magnification", x = "Baseline Score", y = "Gains")
```

```{r}
samp <- MASS::mvrnorm(100, mu = c(0,0), Sigma = matrix(c(1,0,0,1), ncol = 2))
samp <- as.data.frame(samp)

p3<- ggplot(samp, aes(x = V2, y = V1)) + geom_point() + geom_smooth(method = "lm") +
  labs(x = "Baseline Score", y = "Post-Test")
```

```{r}
samp <- MASS::mvrnorm(100, mu = c(0,0), Sigma = matrix(c(1,0.8,0.8,1), ncol = 2))
samp <- as.data.frame(samp)

p4 <- ggplot(samp, aes(x = V2, y = V1)) + geom_point() + geom_smooth(method = "lm") +
  labs(x = "Baseline Score", y = "Post-Test")
```

```{r}
grid.arrange(p1,p2,p3,p4, ncol = 2)
```

### Models

__Model 1:__ 3-Level Random Effects Model

$$\hat{\theta}_{ij} = \theta_{ij} + \epsilon_{ij}$$

$$\theta_{ij} = \kappa_i + \zeta_{(2)ij}$$

$$\kappa_j = \beta_0 + \zeta_{(3)j}$$

__Model 2:__ 3-Level Mixed Effects Model (proposed)

$$\hat{\theta}_{ij} = \theta_{ij} + \epsilon_{ij}$$

$$\theta_{ij} = \kappa_i + \zeta_{(2)ij}$$

$$\kappa_j = \beta_0 + \beta_1(Domain) + \beta_2(Approach) + \zeta_{(3)j}$$

__Model 2a:__ 3-Level Mixed Effects Model (conducted)

$$\hat{\theta}_{ij} = \theta_{ij} + \epsilon_{ij}$$

$$\theta_{ij} = \kappa_i + \zeta_{(2)ij}$$

$$\kappa_j = \beta_0 + \beta_1(Domain/Approach) + \zeta_{(3)j}$$

Data
===
Column
---
### Table

Correlation coefficients are standardized by Fisher's Z as well as by a *-1 transformation such that a positive correlation indicates magnification and a negative correlation indicates compensation.


```{r dataTable}
datatable(df)
```

Column {.tabset}
---
### Cook's D

```{r}
#cooks d claculations
f <- cooks.distance(res.ml)
nam <- names(f)
dis <- as.numeric(f)
m <- data.frame(nam, dis)

#plot
ggplotly(ggplot(m, aes(x = nam, y = dis, group = 1)) + geom_point() + geom_line() + 
  geom_hline(yintercept = (4/nrow(m)), color = "red") +
  theme(axis.text.x = element_text(angle = 65, hjust = 1)) + ylab("Cook's Distance") + xlab(""))
```

### Baujat Plot

__NOTE:__ Tested on non-multilevel model. Relationship of observations within paper not accounted for.

```{r}
res <- rma(yi, vi, slab=paste(paper), data=dat)
baujat(res, symbol = "slab")
```

Bias
===
Column{.tabset}
---
### Funnel: All Effect Sizes

```{r}
funFunnel(res.ml)
```

### Funnel: Aggregated Effect Sizes

```{r}
funFunnel(resAgg)
```

### Sunset Funnel

```{r}
viz_sunset(res.ml)
```

Column
---

### Egger's Regression: Disaggregated

```{r}
regtest(res)
```

### Egger's Regression: Aggregated

```{r}
regtest(resAgg)
```

Model1
===
Column{.sidebar}
---

### Select Ordering

```{r}
selectInput("forest_sort", label = "Sort order",
                              choices = c("weight (1/variance)" = "variances",
                                          "effect size" = "effects",
                                          #"model estimate" = "estimate",
                                          "alphabetical" = "short_cite"))
```

Column
------

### Forest Plot

```{r}
renderPlotly({forest(input$forest_sort, res.ml)})
```

Column
---
### Meta-Correlation Coefficient

```{r}
res.ml
```

__I^2 Heterogenity__

```{r}
#Break down variance by Levels
p<-variance.distribution.3lm(data = dat,
                          m = res.ml)

p[[2]]
```

Model2
===
Column{.sidebar}
---

### Select Ordering

```{r}
selectInput("forest_sort2", label = "Sort order",
                              choices = c("weight (1/variance)" = "variances",
                                          "effect size" = "effects",
                                          "model estimate" = "estimate",
                                          "alphabetical" = "short_cite"))
```

Column
------

### Forest Plot

```{r}
renderPlotly({forest(input$forest_sort2, res.me)})
```

Column
---
### Meta-Regression

```{R}
res.me <- rma.mv(yi, vi, 
                 mods = ~factor(construct),
                 random = list(~1 |id, ~1 | paper), slab=paste(paper), 
                 data=dat); res.me
```

__I^2 Heterogenity__

```{r}
p<-variance.distribution.3lm(data = dat,
                          m = res.me)

p[[2]]
```

Model 3-EF only
===
Column{.sidebar}
---
### Select Ordering

```{r}
selectInput("forest_sort3", label = "Sort order",
                              choices = c("weight (1/variance)" = "variances",
                                          "effect size" = "effects",
                                          "alphabetical" = "short_cite"))
```

Column
------
### Forest Plot

```{r}
renderPlotly({forest(input$forest_sort3, res.EF)})
```

Column{.tabset}
---
### Meta-Regression

```{R}
datEF <- dat %>%
  filter(construct == "EF")

res.EF <- rma.mv(yi, vi, 
                 random = list(~1 |id, ~1 | paper), slab=paste(paper), 
                 data=datEF); res.EF
```

__I^2 Heterogenity__

```{r}
p<-variance.distribution.3lm(data = datEF,
                          m = res.EF)

p[[2]]
```

__Egger's Regression__

```{r}
res <- rma(yi, vi, slab = paste(paper), data = datEF)
regtest(res)
```

### Funnel

```{r}
funFunnel(res)
```

Refrences
===
Column 
---
### Resources

* Analyses primarily conducted using the `metafor` package: https://www.metafor-project.org/doku.php/metafor
* Reactive forest plot and interactive funnel plots based on code from the Standford MetaLab: http://metalab.stanford.edu/
